Numerical simulation of the Cordilleran ice sheet \\ through the last glacial cycle

### 2014-06-30 kappa.tex
Commit work in progress on introduction.

>>>>

In our daily lives, most of us experience ice as a solid that crackles at the
contact with warmer liquids. However, at geologic time scales, ice behaves in a
widely different way. Under the action of precipitation, ice accumulates in the
mountains and cold regions of the globe. Once a critical mass is attained, it
flows down by gravity, thus behaving as a fluid (\cref{fig:glacier-mechanics}).

Glaciers, these bodies of moving ice, shape the landscape, thus leaving traces
of their presence to the eye of the geologist \cref{fig:glaciation-indicators}.
However it was not until XXXX, that these traces were associated with
climatic fluctuations at the scale of the planet. There have been extensive studies investigating the formation and the influence of glaciers on morphology and changes of the earth surface.
